学術論文

### 2021-06-28 articles.Rmd
update
著者数やばい

- [33] Shimono, Y., Hasegawa, A., Tsuchihara, K., Tanaka, K., Matsuda, Y., & Kunisato, Y.(in press) Longitudinal association between autistic traits and affinity for hikikomori in Japanese university students. Current Psychology,

@@

- [32] van Doorn, J., van den Bergh, D., Dablander, F., van Dongen, N., Derks, K., Evans, N., Gronau, Q., Haaf, J., Kunisato, Y., Ly, A., Marsman, M., Sarafoglou, A., Stefan, A., & Wagenmakers, EJ.(2011) Strong public claims may not reflect researchers' private convictions. Significance, 18(1), 44-45.

>>>>

- [34] Wang, K., Goldenberg, A., Dorison, C., Miller, J. K. P., Uusberg, A., Lerner, J. S., Gross, J., Marcu, G. M., Agadullina, E., Adamkovic, M., Roczniewska, M., Kassianos, A., Dursun, P., Arinze, A. I., Arinze, N. C., Ogbonnaya, C., Ndukaihe, I. L. G., Dalgar, I., Akkas, H., Macapagal, P. M. L., Lewis, S., Metin-Orta, I., Willis, M., Santos, A. C., Mokady, A., Reggev, N., Vasilev, M. R., Nock, N. L., Parzuchowski, M., Barría, M. E., Vranka, M. A., Ropovik, I., Yao, X., Becker, M., Manunta, E., Kaminski, G., Findor, A., Lewis, D. M. G., Aruta, J. J. B. R., Zickfeld, J., Vásquez, J. C., Pronizius, E., Lamm, C., Li, R., Valentova, J. V., Mioni, G., Cellini, N., Chen, S.-C., Moon, K., Azab, H., Todsen, A. L., van Schie, K., Bavolar, J., Warmelink, L., Ross, R. M., Stephen, I. D., Hostler, T., McCarthy, R. J., Grano, C., Singh Solorzano, C., Kácha, O., Arvanitis, A., Xiao, Q., Cárcamo, R., Zorjan, S., Tajchman, Z. J., Vilares, I., Pavlacic, J. M., Kunst, J. R., Tamnes, C. K., Atari, M., Sharifian, M., Hricova, M., Kačmár, P., Rahal, R.-M., Zakharov, I., Koehn, M. A., Esteban Serna, C., Hajdu, N., Calin-Jageman, R., Krafnick, A. J., Očovaj, S. B., Khosla, M., Urban, J., Boudesseul, J., Silva, J., Martončik, M., Šakan, D., Kuzminska, A., Djordjevic, J. M., Almeida, I. A. T., Lazarevic, L. B., Manley, H., Zambrano, D., Monteiro, R. P., Musser, E. D., Dunleavy, D. J., Godbersen, H., Ruiz-Fernandez, S., Reeck, C., Batres, C., Azevedo, F., Alvarez, D. S., Chen, Z., Verbruggen, F., Ziano, I., Tümer, M., Dubrov, D., Karababa, A., del Carmen, M., Aberson, C., Moller, A. C., Hubená, B., Ceary, C., Singer, G. A., Perillo, J. T., Ballantyne, T., Du, H., Pit, I. L., Hruška, M., Sousa, D., Aczel, B., Szaszi, B., Barzykowski, K., Micheli, L., Zsido, A. N., Paruzel-Czachura, M., Bialek, M., Kowal, M., Sorokowska, A., Misiak, M., Arriaga, P., Oliveira, R. A., Vaughn, L. A., Szwed, P., Kossowska, M., Kielińska, J., Antazo, B. G., Stieger, S., Nilsonne, G., simonovic, N., Taber, J. M., Gourdon-Kanhukamwe, A., Domurat, A., Ihaya, K., Yamada, Y., Urooj, A., Gill, T., Bylinina, L., Baklanova, E., Albayrak-Aydemir, N., Kappes, H. B., Gjoneska, B., House, T., Berkessel, J., Muda, R., Chopik, W. J., Çoksan, S., Seehuus, M., Khaoudi, A., Azouaghe, S., Arabi, K. A. E., Djamai, I., Wilson, J. P., Adiguzel, A., Kocalar, H. E., Norton, J., Papadatou-Pastou, M., Evans, K., Chuan-Peng, H., De la Rosa-Gomez, A., Ankushev, V., Bogatyreva, N., Grigoryev, D., Ivanov, A., Prusova, I., Romanova, M., Sarieva, I., Terskova, M., Hristova, E., Janak, A., Schei, V., Sverdrup, T. E., Askelund, A. D., Collins, W. M., Boucher, L., Ouherrou, N., Schrötter, J., Bokkour, A., Say, N., Sinkolova, S., Janjić, K., Stojanovska, D., Bijlstra, G., Mosannenzadeh, F., Reips, U.-D., Baskin, E., Ishkhanyan, B., Czamanski-Cohen, J., Dixson, B., Moreau, D., Sutherland, C., Noone, C., Anne, M., Janssen, S. M. J., Fu, C. H., Majeed, N. M., Kunisato, Y., Daches, S., Hartanto, A., Vdovic, M., Forbes, P., Kamburidis, J., Rachev, N. R., Stoyanova, A., Marinova, E., Schmidt, K., Suchow, J. W., Koptjevskaja-Tamm, M., Jernsäther, T., Olofsson, J., Bialobrzeska, O., Marszalek, M., Tatachari, S., Afhami, R., Law, W., Zuro, B., Van Doren, N., Soto, J., Searston, R. A., Miranda, J. F., Yeung, S. K., Krupić, D., Jaeger, B., Ren, D., Pfuhl, G., Klevjer, K., Vally, Z., Vargas-Nieto, J. C., Corral-Frías, N. S., Frias-Armenta, M., Lucas, M. Y., Torres, A. O., Toro, M., Vega, D., Solas, S. Á., Vilar, R., Massoni, S., Reyna, C., Pöntinen, S. J., Adetula, G. A., Foroni, F. P., Kurfali, M. A., Braun Kohlová, M., Harutyunyan, M., Landry, A. T., Ortiz, M., Voracek, M., Grinberg, M., Vintr, J., Kaliska, L., Pourafshari, R., Geiger, S. J., Beitner, J., Szala, A., Anjum, G., von Bastian, C. C., Cohen, N., Kirgizova, K., Muminov, A., Butt, M. M., Lee, J. M., Charyate, A., Sacakli, A., Richard, K., Cyrus-Lai, W., Fedotov, M., Wielgus, M., Adamus, S., Mola, D., Correa, P. S., Belaus, A., Muchembled, F., Ribeiro, R. R., Abbas, N., Čadek, M., Messerschmidt, J., Adetula, A., Kadreva, V., Bran, A., Vaidis, D. C., Vieira, L., Coelho, G. L. H., Whitt, C. M., Tullett, A. M., Du, X., Volz, L., Sarioguz, E., Korbmacher, M., Lima, T., Ribeiro, M. F. F., Verharen, J., Karekla, M., Jaremka, L. M., Storage, D., Studzinska, A., Hanel, P. H. P., Holford, D. L., Sirota, M., Wolfe, K., Chiu, F., Theodoropoulou, A., Ahn, E. R., Lin, Y., Westgate, E. C., Hofer, G., Vezirian, K., Travaglino, G. A., Marko, D., Li, M., Torunsky, N., Manavalan, M., Song, X., Walczak, R. B., Zdybek, P., Dalla Rosa, A., Kozma, L., Alves, S. G., Correia, R., Pinto, I. R., Babincak, P., Baník, G., Varella, M. A. C., Uttley, J., Beshears, J., Thommesen, K. K., Behzadnia, B., Bradford, M., Geniole, S., Silan, M. A., Vilsmeier, J. K., Tran, U. S., Morales-Izquierdo, S., Mensink, M. C., Groyecka-Bernard, A., Sorokowski, P., Radtke, T., Özdoğru, A. A., Ishii, T., Wichman, A. L., Röer, J. P., Ostermann, T., Davis, W. E., Suter, L., Ferreira, A., Agesin, B. B., Rana, K., Eudave, L., Campos, O., Grzech, K., Hausman Ozery, D., Jackson, E. A., Jimenez-Leal, W., Krizanic, V., Garcia, E. O. L., Drexler, S. M., Jurković, A. P., Štrukelj, E., Antoniadi, M., Desai, K., Gialitaki, Z., Kushnir, E., Nadif, K., Bravo, O. N., Nauman, R., Oosterlinck, M., Pantazi, M., Pilecka, N., Szabelska, A., van Steenkiste, I. M. M., Filip, K., Bozdoc, A. I., Westerlund, M., Ahlgren, L., Wang, C., Levy, N. L., Beaudry, J. L., Samojlenko, L., Isager, P. M., Chou, W., Pálfi, B., Schmidt, N.-D., Ortiz, M. V., Czarnek, G., Jones, M., Berkessel, J. B., Iyer, A., Parashar, N., Bundt, C., Pineda, L. M. S., Thomas, A. G., Kung, F. Y. H., Balci, B. B., Flowe, H. D., Topor, M., Yu, K., Anton-Boicuk, L., Kurfalı, M., Antfolk, J., Damnjanović, K., Hoyer, K., Galindo-Caballero, O. J., Calderón Pérez, L., Delgado, G. J., Frizzo, T., Capizzi, M., Greenburgh, A., Bosma, M., Karaarslan, C., Allred, T. B., Colloff, M. F., Karashiali, C., Sunami, N., Habib, S., Hassan, W., Brohmer, H., Dujols, O., Feldman, G., Ahmed, A., Bosch, J., Bai, H., Friedemann, M., Rojas-Berscia, L. M., Maturan, P. L. G., Walasek, L., Adoric, V. C., Carpentier, J., Joy-Gaba, J. A., Zabel, C., Ebersole, C. R., Chartier, C. R., Mallik, P. R., Urry, H. L., Buchanan, E. M., Coles, N. A., Primbs, M., Basnight-Brown, D., IJzerman, H., Forscher, P. S., & Moshontz, H., (in press).
A multi-country test of brief reappraisal interventions on emotions during the COVID-19 pandemic. 
Nature Human Behaviour.

@@

- [33] Shimono, Y., Hasegawa, A., Tsuchihara, K., Tanaka, K., Matsuda, Y., & Kunisato, Y.(2021) Longitudinal association between autistic traits and affinity for hikikomori in Japanese university students. Current Psychology. https://doi.org/10.1007/s12144-020-01287-x

- [32] van Doorn, J., van den Bergh, D., Dablander, F., van Dongen, N., Derks, K., Evans, N., Gronau, Q., Haaf, J., Kunisato, Y., Ly, A., Marsman, M., Sarafoglou, A., Stefan, A., & Wagenmakers, EJ.(2011) Strong public claims may not reflect researchers' private convictions. Significance, 18(1), 44-45.[Pre Print](https://psyarxiv.com/pc4ad/)
